%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Ekumen Labs} % Organization
    {Remote} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consultant for Tier-1 US software development company in the high-paced team.}
        \item {Applying Scrum methodologies to software development.}
        \item {Working in the frontend team helping with the development of new features for the application.}
        \item {Make short presentations about the new features that are available to use to the rest of the team.}
        \item {Responsible for creating technical documentation.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
{Internal Work} % Job title
{} % Organization
{}  % Location
{Dec. 2021 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Migrate old AngularJS messaging project to React.}
    \item{Collaborate by solving bugs in an internal project (React and NodeJS) used for handling holidays, days off and much more.}
    \item{Started training as a Project Lead.}
    \item{Started creating a Three.JS workshop to be taught to internal employees.}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Sr. Quantitative Analyst} % Job title
    {Crisil Limited} % Organization
    {Buenos AIres, Argentina}  % Location
    {Jun. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consultant for Tier-1 US investment bank in the Wealth Management Division.}
        \item {Working with a vendor (third-party) model that uses deep learning techniques in order to price stocks and gain insight into portfolio management investing.}
        \item {Responsible for creating technical documentation.}
        \item {Creation and execution of benchmarking analysis, back testing, stress and stability tests, among others.}
        \item {Engage on weekly model updates and discussions with vendor and bank associates.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quantitative Researcher} % Job title
    {} % Organization
    {} % Location
    {Mar. 2019 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item{Working in a R\&D team in the development of a high-performance library designed to achieve fast and advanced quantitative finance calculations, including: Monte Carlo universal pricing engine for exotic equity products; Greeks computation via automatic differentiation; domain specific language (DSL) design and implementation for syntactically-sweetened inputs.}
          \item{Development of cutting edge Machine Learning and Deep Learning solutions for pricing products with early exercise features in both high and low dimensions.}
          \item {Technical leader in charge of the development, maintenance, testing, documentation and deployment of web applications using high standards for microservice deliveries, including: frontend development; backend development; GraphQL API endpoints; documenting solution architecture; automated cloud migration environments.}
          \item{Responsible for creating a rapidly working prototype by designing the frontend interface using \href{https://reactjs.org/}{React.js} and communicating via \href{https://graphql.org/}{GraphQL} APIs to a \href{https://www.djangoproject.com/}{Django} backend that consumes \href{https://julialang.org/}{Julia} workers.}
          \item{Preparing presentations of technical advances to senior management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quantitative Analyst} % Job title
    {} % Organization
    {} % Location
    {Aug. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Consultant for Tier-1 US investment bank - Equity and Hybrids Group. Front Office.}
        \item {Pricing and Risk Management Equity and Hybrid (IR/FX/COMM) exotic financial derivative models for a Tier-1 US Investment Bank.}
        \item {Responsible for creating technical documentation and generating executive summary reports in \LaTeX.}
        \item{Scrutiny of pricing methodology, model soundness and test suite design. Creating and executing calibration, benchmarking, computational performance, hedging, limiting cases, stability and convergence tests using C\#/Excel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Physicist} % Job title
    {Institute of Physics of Liquids and Biological Systems (IFLySiB) \href{https://mattborghi.github.io/projects/MSc\%20Thesis/}{\faGithub}} % Organization
    {La Plata, Buenos Aires, Argentina} % Location
    {Aug. 2016 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {MSc. in Physics graduate dissertation: Study of phase transitions of an Ising-type model with spin oriented dependent interaction parameters.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {National University of La Plata (UNLP)} % Organization
    {La Plata, Buenos Aires, Argentina} % Location
    {Sep. 2015 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for teaching fundamental physical concepts such as Classical Mechanics and Electromagnetism to undergraduate students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Project Collaborator} % Job title
    {Argentine Institute of Radio Astronomy (IAR) \href{https://mattborghi.github.io/projects/ALAMBRE/}{\faGithub}} % Organization
    {Berazategui, Buenos Aires, Argentina} % Location
    {Nov. 2014 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
           \item {Responsible for the development of a software package that assess the possibility of radio emission detections from extensive air showers induced by cosmic rays.}
          \item {This work was presented as a poster at the 100th Annual meeting of the \emph{Argentine Physics Association} (\href{https://www.fisica.org.ar/}{AFA}) from the 22nd to 25th of September of 2015 in Villa de Merlo, San Luis, Argentina.}
    %       \begin{cvsubentries}
    %     \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
    %     \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
    %   \end{cvsubentries}
      \end{cvitems}
    }
 
%---------------------------------------------------------
\end{cventries}
