%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-concrete}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\newcommand{\myname}{Matias P.}
\newcommand{\mysurname}{Borghi Orue}
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,right]{profile}
\name{\myname}{\mysurname}
\position{Full-Stack Developer {\enskip\cdotp\enskip} MSc. Physics}
\address{Av Cordoba 6570, Chacarita, 1427, CABA, Buenos Aires, Argentina}

\mobile{(+54) 9 11 2157-6504}
\email{borghi.matias@gmail.com}
\homepage{mattborghi.github.io}
\github{mattborghi}
\linkedin{borghimatias}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\newcommand{\company}{Preply}
\newcommand{\job}{Senior Backend Engineer (Python)}

\recipient
  {Company Recruitment Team}
  {\company \\ 1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for \job @ \company}
% How the letter is opened
\letteropening{To Whom It May Concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {\myname {} \mysurname~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{Introduction}
Physicist with 4y+ of professional experience in the finance industry and, in particular, in a R\&D team, looking for a career change into software development which is what I really love doing.


\lettersection{Why \company?}
During my previous role at Crisil, I have been working as a quantitative researcher/developer making high quality libraries but given that my current employer wasn't much interested in changing their line of business, the project didn't continue and right now I find myself doing consulting. Having deeply thought about my career plan, I decided to follow my passion and that's where I found \company. Also, given that I am looking for a relocation opportunity in addition to the fact that I love software development, I didn't think twice about applying for the job position.


\lettersection{Why Me?}
Although I have been programming since I am 15y old, I have found myself with some working challenges that I certainly loved and with a little bit of self-confidence and determination I could arrive to successful outcomes of projects deliverables maintaining always the highest quality and standards. For example, during the years working as a quantitative developer, I formed a really good interdisciplinary collaborative team that worked flawlessly independently or in small groups in order to achieve the project goals. There, I offered myself to do a web app demo that had to be done in record-time in order to be presented in a conference and, having a very basic understanding about front-end development, I was able to develop an excellent platform surpassing all expectations. 

As a person that likes to keep learning continuously I find myself doing online courses and, lately, motivated by the pandemics, attending conferences or talks of interest. Right now, I am trying to take my knowledge on micro-services and Full Stack tech into AI by studying MLOps.

I would enjoy having the opportunity to discuss my application with you and how I could use my skills to benefit \company.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
